\texttt{MSnbase}, efficient and elegant R-based processing and visualisation of raw mass spectrometry data

### 2020-04-30 msnbase2.Rnw
mention testing - closes #7

As is custom with Bioconductor packages, \texttt{MSnbase} comes with
ample documentation. Every user-accessible function is documented in a
dedicated manual page. In addition, the package offers 5 vignettes,
including one aimed at developers. Questions from users and developers
are answered on the Bioconductor support forum as well as on the
package GitHub page. The package provides several sample and
benchmarking datasets, and relies on other dedicated
\textit{experiment packages} such as \texttt{msdata}~\cite{msdata} for
raw data or \texttt{pRolocdata}~\cite{Gatto:2014a} for quantitative
data. \texttt{MSnbase} is available on Windows, Mac OS and Linux under
the open source Artistic 2.0 license and easily installable using
standard installation procedures.

>>>>

As is custom with Bioconductor packages, \texttt{MSnbase} comes with
ample documentation. Every user-accessible function is documented in a
dedicated manual page. In addition, the package offers 5 vignettes,
including one aimed at developers. The package is checked nightly on
the Bioconductor servers: it implements unit tests covering 72\% of
the code base and, through its vignettes, also provides integration
testing. Questions from users and developers are answered on the
Bioconductor support forum as well as on the package GitHub page. The
package provides several sample and benchmarking datasets, and relies
on other dedicated \textit{experiment packages} such as
\texttt{msdata}~\cite{msdata} for raw data or
\texttt{pRolocdata}~\cite{Gatto:2014a} for quantitative
data. \texttt{MSnbase} is available on Windows, Mac OS and Linux under
the open source Artistic 2.0 license and easily installable using
standard installation procedures.
